%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ExperienceSection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Experience
{Teaching Assistant}
{Waseda University}
{September 2025 -- Present}
{Tokyo, Japan}
{
\item Assisted undergraduate students with Fluid Dynamics and Thermodynamics.

\item Guided students through analytical problem solving and engineering
applications.

\item Supported laboratory sessions, assignments and tutorials.

\item Helped improve students' conceptual understanding of mechanical
engineering fundamentals.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Experience
{Engineering Intern}
{Mitsubishi FUSO Truck and Bus Corporation}
{September 2024 -- January 2025}
{Kawasaki, Japan}
{
\item Supported inventory management and warehouse operations.

\item Developed internal databases for project management.

\item Prepared weekly engineering progress reports.

\item Worked with cross-functional teams to improve operational efficiency.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Experience
{Research Intern}
{Team for Advanced Flow Simulation and Modeling (TAFSM)}
{April 2024 -- September 2024}
{Tokyo, Japan}
{
\item Performed Computational Fluid Dynamics simulations.

\item Investigated compressible flow and shock-wave behaviour.

\item Assisted researchers in numerical modelling and validation.

\item Analysed CFD results using Python and ParaView.

\item Contributed to research on isogeometric fluid analysis.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Experience
{Physics Tutor}
{ISM Institute}
{January 2020 -- January 2022}
{Colombo, Sri Lanka}
{
\item Conducted individual and group tutoring sessions.

\item Explained advanced mechanics and electromagnetics concepts.

\item Designed practice questions and examination material.

\item Improved student performance through personalised teaching methods.
}